WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2018-12-11 paper/ms.tex
update figures per JNW comments

The second process that long-term timing studies should reveal is
rotation of the orbital ellipse within the orbital plane (apsidal
precession).  This effect has been studied extensively in eclipsing
binaries \citep[{\it e.g.},][]{
  schwarzschild_structure_1958,torres_accurate_2010,borkovits_eclipse_2015},
and has been explored theoretically for transiting planets
\citep{heyl_using_2007,pal_periastron_2008,jordan_observability_2008,ragozzine_probing_2009}.
However, apsidal precession has yet to be directly observed in hot
Jupiters, and the orbits would need non-zero eccentricity for it to be
detectable.  Though the eccentricities of hot Jupiters are expected to
be small, there are many mechanisms that could pump them away from
circularity (see \S~\ref{sec:apsidal_precession}, and
\citealt{bailey_understanding_2019}).  For hot Jupiters, the apsidal
precession is usually dominated by the quadrupolar distortion of the
planet by the star's tidal force \citep{ragozzine_probing_2009}.  The
observed precession rate in a hot Jupiter system can thus be used to
compute the planet's Love number, giving a third parameter along with
the mass and radius with which to describe the planet's interior
structure \citep[{\it e.g.},][who performed a similar procedure for
HAT-P-13b]{batygin_determination_2009}.  Measuring small
eccentricities and understanding their origin might also help us
understand the dynamical histories and inflated radii of hot Jupiters.
\citep[{\it
e.g.},][respectively]{dawson_origins_2018,ibgui_tidal_2010}

@@

This work focuses on the hot Jupiter WASP-4b, which orbits its host
star every 1.34 days, at a distance of $a/R_\star = 5.46$
\citep{wilson_wasp-4b_2008,hoyer_tramos_2013}.  WASP-4b is a plausible
candidate for orbital decay, in part because it has been frequently
observed over the past decade.  The host is a G7V dwarf, and is on the
main sequence (\S~\ref{sec:system_parameters}).  The orbit is
consistent with being circular (but see
\S~\ref{sec:apsidal_precession}), and having sky-projected obliquity
of zero
\citep{triaud_spin-orbit_2010,beerer_secondary_2011,sanchis-ojeda_starspots_2011}.

@@

\begin{figure}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.48\textwidth]{f2.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
      %TODO: final number
        {\bf TESS saw WASP-4b transit earlier than expected.}
        Points are differences between observed transit times and the
        constant-period ephemeris we fit to literature times.  Black
        points are the more precise half of literature times; gray
        points are the less precise half.  Blue curves represent the
        $\pm 1\sigma$ credible interval around the constant-period
        ephemeris.  The binned TESS observation (red point) arrived
        $77.8 \pm 10.8\ {\rm seconds}$ before it was expected.
        \label{fig:arrived_early}
    }
\end{figure}

@@

\begin{figure*}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.9\textwidth]{f3.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        {\bf Timing residuals and best-fit models for WASP-4b.}
        Points are differences between observed transit times and a
        linear ephemeris fit to all the times.  The constant period
        model is a poor fit to the observed times (gray line).  Black
        points are the more precise half of measured times; gray
        points are the less precise half.  The blue curve is the
        best-fit model with a constant period derivative.  The orange
        curve is the best-fit model assuming apsidal precession causes
        the observed timing deviations. The binned TESS point (star)
        is for display purposes only.
        \label{fig:times}
    }
\end{figure*}

@@

There are fewer available occultation times.
\citet{beerer_secondary_2011} observed two occultations of WASP-4b
using warm Spitzer in the 3.6\,$\mu$m and 4.5\,$\mu$m bands.
\citet{caceres_ground-based_2011} detected an occultation from the
ground in the ${\rm K}_{\rm s}$ band, and gave a time in HJD, without
specifying the time standard.  We correspondingly added $69.184$
seconds of uncertainty to their reported errors, in quadrature.
%Finally, as previously mentioned, \citet{ranjan_atmospheric_2014}
%acquired occultation data with HST but kept the epoch as a fixed
%parameter.
\citet{zhou_secondary_2015} acquired occultation data from the
Anglo-Australian Telescope, focusing on the eclipse depth, but also
fitting for $e\cos\omega$.  We converted their $e\cos\omega$ result
into a midtime, using their ephemeris and the standard formula
\citep[{\it e.g.},][]{winn_exoplanet_2010}
\begin{equation}
  t_{\rm occ}(E) =
  t_0 +  P E  +
  \frac{P}{2} \left( 1 + \frac{4}{\pi} e\cos\omega \right).
  \label{eq:occultation_time}
\end{equation}
This gives us a total of 4 occultations.  Although the occultation
times are uncertain compared to the transits, they nonetheless help in
modeling the timing variations.

@@

The middle panel of Figure~\ref{fig:context} shows the expected
orbital decay time of WASP-4b compared to other transiting giant
planets.  Though roughly 20 hot Jupiters might be expected to decay
faster, some orbit stars with minimal convective zones ({\it e.g.},
WASP-18), and most are not as well-observed as WASP-4.

For the sake of argument, let us assume that the timing variation is
caused entirely by orbital decay.  If the period continues to decrease
at a fixed rate, it will reach zero after
\begin{equation}
  \frac{P}{ \dot{P} } = 9.6 \, {\rm Myr}.
\end{equation}
For comparison, the ``survival time'' found by \citet{patra_2017} for
WASP-12b was 3.2\,Myr.

Let us assume further that the ``constant phase lag'' model for tidal
interaction in a binary applies \citep{zahn_tidal_1977}.  The fluid
response is parametrized by a modified\footnote{For stars, $k_\star
\sim \mathcal{O}(10^{-2})$, so it is important to explicitly
distinguish $Q_\star'$ from $Q_\star$ \citep[{\it
e.g.},][]{schwarzschild_structure_1958}.} quality factor, $Q_\star' =
3 Q_\star / (2k_\star)$.  Here $k_\star$ is the stellar Love number,
which is smaller when the star's density distribution is more
centrally concentrated. $Q_\star$ is the ratio of the energy stored in
the equilibrium deformation of the star, divided by the energy lost to
heat per tidal period \citep[{\it e.g.},][]{goldreich_q_1966}.  A
larger $Q_\star$ implies less efficient dissipiation.  Though the
fluid mechanics responsible for the dissipation should depend on the
amplitude and frequency of the tidal perturbation
\citep[][Section~3.3]{ogilvie_tidal_2014}, we will treat $Q_\star'$ as
a constant.  This should not be taken literally; $Q_\star'$ may in
fact change sharply with varying tidal frequency
\citep{penev_empirical_2018}.

If the planet's spin and orbit are synchronized, the star is slowly
rotating, and the eccentricity is small, then the semi-major axis and
eccentricity evolve as \citep[Appendix B of][]{metzger_optical_2012}
\begin{align}
  \frac{1}{\tau_{\rm e}} &=
  \frac{|\dot{e}|}{e} =
    \frac{63 \pi } {2 Q_{\rm p}' }
    \left( \frac{R_{\rm p}}{a} \right)^5
    \left( \frac{M_\star}{M_{\rm p}} \right)
    \left( \frac{1}{P} \right)
  \label{eq:de_dt}
  \\
  \frac{1}{\tau_{\rm a}} &=
  \frac{|\dot{a}|}{a} =
    \frac{9 \pi } {Q_\star' }
    \left( \frac{R_\star}{a} \right)^5
    \left( \frac{M_{\rm p}}{M_\star} \right)
    \left( \frac{1}{P} \right).
  \label{eq:da_dt}
\end{align}
The orbital period evolves as
\begin{equation}
\label{eq:dP_dt}
  \dot{P} = -\frac{27\pi}{2 Q_\star'}
            \left(\frac{M_{\rm p}}{M_\star}\right)
            \left(\frac{R_\star}{a}\right)^5.
\end{equation}
Using the observed value of $\dot{P}$, the current modified quality
factor of WASP-4 would be
\begin{equation}
	Q_\star' \approx 3.3\times10^4. 
\end{equation}
This is rather small.  Jupiter has $Q_{\rm Jup}' \approx 1.4 \times
10^5$, based on the orbits of the Galilean moons
\citep{lainey_strong_2009}.  For stars, studies of the binary
eccentricity distribution have yielded $Q_\star' \approx 10^5 - 10^7$
\citep[{\it e.g.},][]{meibom_robust_2005,belczynski_compact_2008,
geller_direct_2013,milliman_wiyn_2014}.  However the dissipation rates
may differ in hot Jupiter systems, since the tidal forcing frequencies
and amplitudes are different.  Observationally-driven studies of hot
Jupiter systems have found $Q_\star' \approx 10^5 - 10^8$, often using
different models
\citep{jackson_observational_2009,hansen_calibration_2010,penev_constraining_2012,penev_empirical_2018,cameron_hierarchical_2018}.
For instance, motivated by the rapid rotation of some hot Jupiter
hosts \citep{pont_empirical_2009,penev_hats-18b_2016},
\citet{penev_empirical_2018} modeled the evolution of hot Jupiter
systems under the influence of a magnetized wind and a constant
phase-lag tide.  For WASP-4, their method gave $Q_\star' \approx
(1.2^{+1.0}_{-0.5})\times10^7$.  This disagrees strongly with the
value we infer from the apparent period change.

@@

A theoretically-motivated model for tidal dissipation was proposed by
\citet{essick_orbital_2016}, who considered the nonlinear response of
the star to a coupled network of gravity modes excited at the base of
the convective zone, and braking near the stellar core.  In their
approach, the stellar quality factors in hot Jupiter systems vary from
$Q_\star' \approx 10^5 - 10^6$.  Using their Equation 26, the
prediction for WASP-4 is $Q_\star' = 7\times10^5$.  This is an order
of magnitude larger than implied by the observed period change.

The applicability of the \citet{essick_orbital_2016} model depends on
the evolutionary state of the star.  The bottom panel of
Figure~\ref{fig:context} shows WASP-4 in the context of other giant
planet hosts from the \citet{bonomo_gaps_2017} sample.  On the y-axis
is $G=g-\mu$, for $g$ the apparent Gaia-band magnitude, and $\mu$ the
distance modulus reported by \citet{gaia_collaboration_gaia_2018}.
The x-axis is the effective temperature from \citet{bonomo_gaps_2017},
which for WASP-4 agrees within $1\sigma$ of that from Table~2.
Inspecting the HR diagram, WASP-4 shows litle evidence of being
evolved, in agreement with our analysis from
\S~\ref{sec:system_parameters}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% By a similar argument though, WASP-12 would not clearly stand out as a
% candidate subgiant, and \citet{weinberg_tidal_2017} suggest it may in
% fact be a subgiant (though \citealt{bailey_understanding_2019} do not
% find evidence that supports this suggestion).  A more thorough
% isochronal analysis would be of interest, particularly if the transit
% and occultation times continue to vary.  Such an analysis is beyond
% the scope of this study.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In short, if the observed period change is caused entirely by tidal
decay, it would imply a tidal dissipation efficiency stronger than
most predictions.  It might be possible that we are observing at a
special time, shortly after the planet's inward migration, or when the
planet is near resonance with a stellar oscillation mode
\citep{ogilvie_tidal_2014,essick_orbital_2016}.  Tidal dissipation
rates might also be increased if the star is turning off the main
sequence.  All of these explanations are strained; it is unclear that
tidal decay could explain the observed timing variations without
fine-tuning.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f5.pdf}
	\end{center}
  \vspace{-0.5cm}
	\caption{
		{\bf Pecise long-term monitoring past 2025 will likely be needed to
	    understand WASP-4b.}
		Dots are as in Figure~\ref{fig:times}.
		Lines are 100 random draws from the posteriors of the apsidal
		precession model (orange), and the orbital decay model (blue).    
		\label{fig:future}
	}
\end{figure}

>>>>

The second process that long-term timing studies should reveal is
apsidal precession, {\it i.e.}, rotation of the orbital ellipse within
the orbital plane. Apsidal precession has been observed extensively in
eclipsing binaries \citep[{\it e.g.},][]{
  schwarzschild_structure_1958,torres_accurate_2010,borkovits_eclipse_2015},
and has been detected in a handful of exoplanet systems, including
circumbinary planets (Kepler-413 \citealt{kostov_kepler-413b_2014};
Kepler-453 \citealt{welsh_kepler_2015}, planets orbiting rapidly
rotating stars (Kepler-13
\citealt{szabo_spin-orbit_2012,szabo_mapping_2014,masuda_spin-orbit_2015};
PTFO 8-8695 \citealt{barnes_measurement_2013}), and systems with
multiple interacting giant planets (Kepler-108
\citealt{mills_kepler-108_2017}; Kepler-693
\citealt{masuda_eccentric_2017}).  Apsidal precession is not regularly
observed in hot Jupiter systems, perhaps in part because their orbits
are nearly circular.  However, there are many mechanisms that
could pump hot Jupiter orbits away from circularity (see
\S~\ref{sec:apsidal_precession}, and
\citealt{bailey_understanding_2019}), which would then lead to
observable timing variations.  For hot Jupiters, the apsidal
precession is usually dominated by the quadrupolar distortion of the
planet by the star's tidal force \citep{ragozzine_probing_2009}.  The
observed precession rate in a hot Jupiter system could thus be used to
compute the planet's Love number, giving a third parameter along with
the mass and radius with which to describe the planet's interior
structure \citep[{\it e.g.},][who performed a similar procedure for
HAT-P-13b]{batygin_determination_2009}.  Measuring small
eccentricities and understanding their origin might also help us
understand the dynamical histories and inflated radii of hot Jupiters.
\citep[{\it
e.g.},][respectively]{dawson_origins_2018,ibgui_tidal_2010}

@@

This work focuses on the hot Jupiter WASP-4b, which orbits its host
star every 1.34 days, at a distance of $a/R_\star = 5.46$
\citep{wilson_wasp-4b_2008,hoyer_tramos_2013}.  WASP-4b is a plausible
candidate for orbital decay, and has been
observed often over the past decade.  The host is a G7V dwarf, and is on the
main sequence (\S~\ref{sec:system_parameters}).  The orbit is
consistent with being circular (but see
\S~\ref{sec:apsidal_precession}), and having sky-projected obliquity
of zero
\citep{triaud_spin-orbit_2010,beerer_secondary_2011,sanchis-ojeda_starspots_2011}.

@@

\begin{figure}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.48\textwidth]{f2.pdf}
    \end{center}
    \vspace{-0.6cm}
    \caption{
      %TODO: final number
        {\bf TESS saw WASP-4b transit earlier than expected.}
        Points are the
        differences between observed transit times and the
        pre-TESS ephemeris, plotted against
        transit number.
        Blue curves are the
        $\pm 1\sigma$ credible interval around the constant-period
        prediction.
        {\it Top:} The full timing dataset spans 10 years.
                Less precise points are more transparent.
        {\it Bottom:}
        The binned TESS observation (red point) arrived
        $77.8 \pm 10.8\ {\rm seconds}$ before it was expected.
        \label{fig:arrived_early}
    }
\end{figure}

@@

\begin{figure*}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.9\textwidth]{f3.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        {\bf Timing residuals and best-fit models for WASP-4b.}
        Points are observed transit times minus a
        linear fit to all the times.
        Less precise times are more transparent.
        The best constant period
        model is a poor fit to the observations (gray line).
        The best-fit tidal decay model (blue) and apsidal precession
        model (orange) can fit the data.
        The binned TESS point (star)
        is for display purposes only.
        \label{fig:times}
    }
\end{figure*}

@@

There are fewer available occultation times.
\citet{beerer_secondary_2011} observed two occultations of WASP-4b
using warm Spitzer in the 3.6\,$\mu$m and 4.5\,$\mu$m bands.
\citet{caceres_ground-based_2011} detected an occultation from the
ground in the ${\rm K}_{\rm s}$ band, and gave a time in HJD, without
specifying the time standard.  We assumed the standard was UTC, but
added $32.182 + N$ seconds of uncertainty to the reported errors,
where $N=35$ is the appropriate number of leap-seconds
\citep[see][]{eastman_achieving_2010}.
Though not rigorous, this procedure inflates the error bar to a more
realistic $\pm$94 seconds.
%Finally, as previously mentioned, \citet{ranjan_atmospheric_2014}
%acquired occultation data with HST but kept the epoch as a fixed
%parameter.
Finally, \citet{zhou_secondary_2015} acquired occultation data from
the Anglo-Australian Telescope, focusing on the eclipse depth, but
also fitting for $e\cos\omega$.  We converted their $e\cos\omega$
result into a midtime, using their ephemeris and the standard formula
\citep[{\it e.g.},][]{winn_exoplanet_2010}
\begin{equation}
  t_{\rm occ}(E) =
  t_0 +  P E  +
  \frac{P}{2} \left( 1 + \frac{4}{\pi} e\cos\omega \right).
  \label{eq:occultation_time}
\end{equation}
This gives us a total of 4 occultations.  Although the occultation
times are uncertain compared to the transits, they nonetheless help in
modeling the timing variations.

@@

The middle panel of Figure~\ref{fig:context} shows the expected
orbital decay time of WASP-4b compared to other transiting giant
planets.  Though roughly 20 hot Jupiters have shorter predicted decay
times, most are not as well-observed as WASP-4b. Moreover, some hot
Jupiters, {\it e.g.}, WASP-18b, orbit fully radiative stars, which may
dissipate tidal energy less efficiently than stars that are partially
convective.

For the sake of argument, let us assume that the timing variation is
caused entirely by orbital decay.  If the period decreases
at a fixed rate, then it will reach zero after
\begin{equation}
  \frac{P}{ \dot{P} } = 9.6 \, {\rm Myr}.
\end{equation}
For comparison, the survival time found by \citet{patra_2017} for
WASP-12b was 3.2\,Myr.

Let us assume further that the ``constant phase lag'' model for tidal
interaction in a binary applies \citep{zahn_tidal_1977}.  The fluid
response is parametrized by a modified\footnote{For stars, $k_\star
\sim \mathcal{O}(10^{-2})$, so it is important to explicitly
distinguish $Q_\star'$ from $Q_\star$ \citep[{\it
e.g.},][]{schwarzschild_structure_1958}.} quality factor, $Q_\star' =
3 Q_\star / (2k_\star)$.  Here $k_\star$ is the stellar Love number,
which is smaller when the star's density distribution is more
centrally concentrated. $Q_\star$ is the ratio of the energy stored in
the equilibrium deformation of the star, divided by the energy lost to
heat per tidal period \citep[{\it e.g.},][]{goldreich_q_1966}.  A
larger $Q_\star$ implies less efficient tidal dissipiation.  Though
the fluid mechanics responsible for the dissipation should depend on
the amplitude and frequency of the tidal perturbation
\citep[][Section~3.3]{ogilvie_tidal_2014}, we will treat $Q_\star'$ as
a constant.  This should not be taken literally; $Q_\star'$ may in
fact change sharply as the tidal frequency changes
\citep{penev_empirical_2018}.

If the planet's spin and orbit are synchronized, the star is slowly
rotating, and the eccentricity is small, then the semi-major axis and
eccentricity evolve as \citep[Appendix B of][]{metzger_optical_2012}
\begin{align}
  \frac{1}{\tau_{\rm e}} &=
  \frac{|\dot{e}|}{e} =
    \frac{63 \pi } {2 Q_{\rm p}' }
    \left( \frac{R_{\rm p}}{a} \right)^5
    \left( \frac{M_\star}{M_{\rm p}} \right)
    \left( \frac{1}{P} \right)
  \label{eq:de_dt}
  \\
  \frac{1}{\tau_{\rm a}} &=
  \frac{|\dot{a}|}{a} =
    \frac{9 \pi } {Q_\star' }
    \left( \frac{R_\star}{a} \right)^5
    \left( \frac{M_{\rm p}}{M_\star} \right)
    \left( \frac{1}{P} \right).
  \label{eq:da_dt}
\end{align}
The orbital period evolves as
\begin{equation}
\label{eq:dP_dt}
  \dot{P} = -\frac{27\pi}{2 Q_\star'}
            \left(\frac{M_{\rm p}}{M_\star}\right)
            \left(\frac{R_\star}{a}\right)^5.
\end{equation}
The modified quality factor of WASP-4 corresponding to the observed
value of $\dot{P}$ would then be
\begin{equation}
	Q_\star' \approx 3.3\times10^4. 
\end{equation}
This is rather small.  Jupiter has $Q_{\rm Jup}' \approx 1.4 \times
10^5$, based on the orbits of the Galilean moons
\citep{lainey_strong_2009}.  For stars, studies of the binary
eccentricity distribution have yielded $Q_\star' \approx 10^5 - 10^7$
\citep[{\it e.g.},][]{meibom_robust_2005,belczynski_compact_2008,
geller_direct_2013,milliman_wiyn_2014}.  The dissipation rates may
differ in hot Jupiter systems, since the tidal forcing frequencies and
amplitudes are different.  Observationally-driven studies of hot
Jupiter systems have found $Q_\star' \approx 10^5 - 10^8$, from quite
different models
\citep{jackson_observational_2009,hansen_calibration_2010,penev_constraining_2012,penev_empirical_2018,cameron_hierarchical_2018}.
For instance, motivated by the rapid rotation of some hot Jupiter
hosts \citep{pont_empirical_2009,penev_hats-18b_2016},
\citet{penev_empirical_2018} modeled the evolution of hot Jupiter
systems under the influence of a magnetized wind and a constant
phase-lag tide.  For WASP-4, their method gave $Q_\star' \approx
(1.2^{+1.0}_{-0.5})\times10^7$.  This disagrees strongly with the
value we infer from the apparent period change.

@@

\citet{essick_orbital_2016} proposed a theoretically-motivated tidal
dissipation model , in which a coupled network of gravity modes would
be excited at the base of the stellar convective zone, and would brake
near the stellar core to provide the needed dissipation.  In their
approach, the stellar quality factors in hot Jupiter systems vary from
$Q_\star' \approx 10^5 - 10^6$.  From their Equation 26, the predicted
quality factor for WASP-4 is $Q_\star' = 7\times10^5$.  This is an
order of magnitude larger than implied by the observed period change.

The applicability of the \citet{essick_orbital_2016} model depends on
the evolutionary state of the star.  The bottom panel of
Figure~\ref{fig:context} shows WASP-4 in the context of giant planet
hosts from the \citet{bonomo_gaps_2017} sample.  On the y-axis is
$G=g-\mu$, for $g$ the apparent Gaia-band magnitude, and $\mu$ the
distance modulus reported by \citet{gaia_collaboration_gaia_2018}.
The x-axis is the effective temperature from \citet{bonomo_gaps_2017},
which for WASP-4 agrees within $1\sigma$ of that from Table~2.
Inspecting the HR diagram, WASP-4 shows litle evidence of being
evolved, in agreement with our analysis from
\S~\ref{sec:system_parameters}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% By a similar argument though, WASP-12 would not clearly stand out as a
% candidate subgiant, and \citet{weinberg_tidal_2017} suggest it may in
% fact be a subgiant (though \citealt{bailey_understanding_2019} do not
% find evidence that supports this suggestion).  A more thorough
% isochronal analysis would be of interest, particularly if the transit
% and occultation times continue to vary.  Such an analysis is beyond
% the scope of this study.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In summary, if the observed period change is caused entirely by tidal
decay, it would imply a tidal dissipation efficiency stronger than
most predictions.  It might be possible that we are observing at a
special time, shortly after the planet's inward migration, or when the
planet is near resonance with a stellar oscillation mode.  Tidal
dissipation rates might also be increased if the star is turning off
the main sequence.  A final possibility is that an exterior planet
could be trapping WASP-4b's spin vector in a high-obliquity state,
causing planetary obliquity tides as suggested for WASP-12b
\citep{millholland_obliquity_2018}.  For now, all of these
explanations seem strained; it is unclear that tidal decay can explain
the observed timing variations by any mechanism that we have
considered.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f5.pdf}
	\end{center}
  \vspace{-0.5cm}
	\caption{
		{\bf Further observations will be needed to
	    confirm and understand the timing variations of WASP-4b.}
		Dots are as in Figure~\ref{fig:times}.
		Lines are 100 random draws from the posteriors of the apsidal
		precession model (orange), and the orbital decay model (blue).    
		\label{fig:future}
	}
\end{figure}
